---
title: "L0-Analysis"
author: "Ben Peloquin"
date: "July 22, 2016"
output:
  html_document:
    toc: true
    toc_depth: 4
---

```{r packages}
library(dplyr)
library(tidyr)
library(ggplot2)
```

Working through experimental set-up
```{r expt_setup}
NUM_ITEMS <- 105
trials <- sample.int(n=NUM_ITEMS, size=NUM_ITEMS)

trial_meta <- function(n) {
  item <- n %% 21
  stars <- n %% 5
  c("item"=item, "stars"=stars)
}

d_trials <- data.frame(t(as.matrix(sapply(trials, trial_meta))))
d_trials <- d_trials %>%
  mutate(stars=stars + 1) %>%
  arrange(item)
```

# Analysis

## Data pre-processing (combine domains, data-typing)
```{r data_preprocessing}
# read.csv()
```

## Plots by scalar pairs and domains
```{r plots1}
# ggplot()
```

## Does domain predict response? Logistic regression

Null hypothesis is there are no differences between domain (i.e. domain should not significantly predict response).
```{r test_domain_differences}
# glm()
```

## Secondary analysis -- any target items appear to be more flexible to `domain` than others???
```{r test_sensitivity}

```
